Automated Topic Naming

### 2012-01-18 ese/ese.tex
more fixes on e.g timeline critiques

We argue for using ROC over F-Measure because ROC suffers less from
bias than F-Measure and as often F-Measure skews towards the positive
class~\cite{flach-icml03,Forman:2010:ACS:1882471.1882479}, especially
in the case of class imbalance. Forman et
al.~\cite{Forman:2010:ACS:1882471.1882479} demonstrate that cross-fold
validation will often produce low F-measures given high class
imbalance and the presence of false negatives.
Although
recent work~\cite{Forman:2010:ACS:1882471.1882479} has suggested that while ROC suffers less bias than
the average F-measure ($F_{avg}$) for cross-folds, F-measures ($F_{tp,fp}$) that are calculated from
the sums of true-positives,
false-positive, and false-negatives across folds tend to exhibit no
bias. Unfortunately our experimental framework lacks a robust way to
calculate $F_{tp,fp}$, thus we still provide ROC and $F_{avg}$.
We consider our labelling classifiers acceptable if they outperform a random classifier (0.5).

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have
quite different results, as the ROC values for \emph{reliability} and
\emph{functionality} swap between projects. For PostgreSQL, the
performance is nearly always poorer than the other two systems. The
reason for this lack of performance could be that the number of
topics, $N$, could be non-optimal for PostgreSQL. Perhaps topics were
getting too mixed and it was becoming hard to distinguish one topic
from the next. PostgreSQL's data-set was the largest of the 3 projects:
the XML data-dump that described the PostgreSQL topics that we
annotated was 8 times larger than MySQL and 1.7 times larger than MaxDB. These
size differences arise from the number of commits, the number of files
and the verbosity of the commit descriptions.

@@

For all projects Bayesian techniques did the best out of a wide variety of machine learners tested. 
Our best learners, Discriminative Multinomial Naive Bayes, Naive Bayes
and Multinomial Naive Bayes  are all based on Bayes' theorem and all
assume, naively, that the features supplied are independent. 
%The features we used are word counts per message. 
One beneficial aspect of this result is that it suggests we can have
very fast training and classifying  since training on or classifying one
instance with Naive Bayes can be calculated in $O(N)$
for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

%\subsection{Timeline analysis}
Topic time-lines are depicted in Figures \ref{fig:mysql-timeline}, 
\ref{fig:maxdb-timeline} and \ref{fig:pgsql-timeline}. These topic time-lines show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
% based on the manually annotated
%topics, although this visualization can be generated from the
%results of labelled topic extraction.
There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to the NFR. 
For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with the NFR per period 
relative to the maximum number of labelled topics overall. 
For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs
\emph{functionality}, \emph{portability} and \emph{maintainability}
contain more labelled topics, since these NFRs have been more
intensely shaded. One interesting stream is \emph{efficiency}, which shows periodic
activity, and suggests that efficiency-related changes
have longer lasting effects.
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.

@@

%For MySQL (Figure \ref{fig:mysql-timeline}), we similarly validated our NFR patterns with external mailing list data. 
The development period of MySQL we studied  (Figure \ref{fig:mysql-timeline}) saw the first releases to be licensed under the GPL. 
Version 3.23.31 (January, 2001) was the production release (non-beta), and the timeline view shows a flurry of topics labelled with \emph{functionality} and
\emph{maintainability}. 
After this point, this version enters the maintenance phase of its life-cycle. 
In May 2001, there is an increase in the number of topics labelled with \emph{portability}. 
This might be related to release 3.23.38, which focused on Windows compatibility. 
Similarly, in August, 2002, both \emph{functionality} and \emph{portability} are frequent, and mailing list data suggests this is related to the release
of version 3.23.52, a general bug fix with a focus on security (a component of the \emph{functionality} NFR in the ISO9126 model). 
After this point, efforts shift to the newer releases (4.0, 4.1,
5.0).

>>>>

We argue for using ROC over F-Measure because ROC suffers less from
bias than F-Measure and F-Measure often skews towards the positive
class~\cite{flach-icml03,Forman:2010:ACS:1882471.1882479}, especially
in the case of class imbalance. Forman et
al.~\cite{Forman:2010:ACS:1882471.1882479} demonstrate that cross-fold
validation will often produce low F-measures given high class
imbalance and the presence of false negatives.
Although
recent work~\cite{Forman:2010:ACS:1882471.1882479} has suggested that while ROC suffers less bias than
the average F-measure ($F_{avg}$) for cross-folds, F-measures ($F_{tp,fp}$) that are calculated from
the sums of true-positives,
false-positive, and false-negatives across folds tend to exhibit no
bias. Unfortunately our experimental framework lacks a robust way to
calculate $F_{tp,fp}$, thus we still provide ROC and $F_{avg}$.
We consider our labelling classifiers acceptable if they outperform a random classifier (0.5).

@@

Figure \ref{fig:best-learn-per-tag} shows that MaxDB and MySQL have
quite different results, as the ROC values for \emph{reliability} and
\emph{functionality} swap between projects. For PostgreSQL, the
performance is nearly always poorer than the other two systems. The
reason for this lack of performance could be that parameter we chose for number of
topics, $N$, could be non-optimal for PostgreSQL. One explanation is that given the size of the PostgreSQL dataset, it was becoming hard to distinguish one topic
from the next. PostgreSQL's data-set was the largest of the 3 projects:
the XML datafile that described the PostgreSQL topics that we
annotated was 8 times larger than MySQL and 1.7 times larger than MaxDB. These
size differences arise from the number of commits, the number of files
and the verbosity of the commit descriptions.

@@

For all projects Bayesian techniques did the best out of a wide variety of machine learners tested, due to the large number of features they can handle.
Our best learners, Discriminative Multinomial Naive Bayes, Naive Bayes
and Multinomial Naive Bayes  are all based on Bayes' theorem and all
assume, naively, that the features supplied are independent. 
%The features we used are word counts per message. 
One beneficial aspect of this result is that it suggests we can have
very fast training and classifying  since training on or classifying one
instance with Naive Bayes can be calculated in $O(N)$
for $N$ features.
%http://nlp.stanford.edu/IR-book/html/htmledition/naive-bayes-text-classification-1.html

@@

%\subsection{Timeline analysis}
Topic time-lines are depicted in Figures \ref{fig:mysql-timeline}, 
\ref{fig:maxdb-timeline} and \ref{fig:pgsql-timeline}. These topic time-lines show the
temporal patterns of NFR frequencies.
%NEIL- I think this (below) is just confusing, although maybe important to note.
This is generated from the manually annotated
topics, although this visualization can be generated from the
results of labelled topic extraction. Note that there are no unlabelled topics in this dataset.

There are two measures represented. 
One, the relative frequency, shown in the grey histogram boxes, represents the number of topics with that NFR in that period, 
relative to the maximum number of topics assigned to the NFR. 
For example, in Figure \ref{fig:mysql-timeline} we see a spike in \emph{portability} and \emph{functionality} frequency in September 2002.
The second, absolute frequency, is shown using cell intensity, and compares the number of topics labelled with the NFR per period 
relative to the maximum number of labelled topics overall. 
For instance, Figure \ref{fig:mysql-timeline} shows that the NFRs
\emph{functionality}, \emph{portability} and \emph{maintainability}
contain more labelled topics, since these NFRs have been more
intensely shaded. One interesting stream is \emph{efficiency} in PostgreSQL, which shows periodic
activity, and suggests that efficiency-related changes
have longer lasting effects. A more systematic analysis of periodicity is necessary to properly conclude this.
The topmost row in each diagram lists historical events for that project (such as a release). 
%We refer to these occurrences in the discussion which follows.

@@

%For MySQL (Figure \ref{fig:mysql-timeline}), we similarly validated our NFR patterns with external mailing list data. 
The development period of MySQL we studied  (Figure \ref{fig:mysql-timeline}) saw the first releases to be licensed under the GPL. 
Version 3.23.31 (January, 2001) was the production release (non-beta), and the timeline view shows a flurry of topics labelled with \emph{functionality} and
\emph{maintainability}. 
After this point, this version enters the maintenance phase of its life-cycle. 
In May 2001, there is an increase in the number of topics labelled with \emph{portability}. 
This might be related to release 3.23.38, which focused on Windows compatibility. 
Similarly, in August, 2002, both \emph{functionality} and \emph{portability} are frequent, and mailing list data suggests this is related to the release
of version 3.23.52, a general bug fix with a focus on security (a component of the \emph{functionality} NFR in the ISO9126 model). 
After this point, efforts shift to the newer releases (4.0, 4.1, 5.0) and subsequently becomes more functionality oriented.
